


### Text mining



### Load Libraries and data
```{r}

library(tidyverse)
library(tidytext)
#library(qdap)

#data <- read.csv("text.data.csv")
data <- read.csv("long.data.csv")
```


### Simple plots
```{r}
level.n <- data %>% filter(level!="?") %>% group_by(Subgenus, level) %>% count(level)

ggplot(level.n, aes(Subgenus,fill=level, y=n)) +  geom_bar(stat="identity", color="black")+scale_fill_manual(values=c("#FF9912","#BDB76B","#65909A")) +theme_bw() +coord_flip() +theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + ylab("count")+ scale_y_continuous(expand = c(0, 0), limits = c(0, 160)) 

habitat.n <- data %>% filter(Habitat!="?") %>% group_by(Subgenus, Habitat) %>% count(Habitat)

ggplot(habitat.n, aes(Subgenus,fill=Habitat, y=n)) +  geom_bar(stat="identity", color="black") +scale_fill_manual(values=c("#BDB76B","#65909A","#FF9912","#A68064","#48426C","#B7C3D0")) +theme_bw() +coord_flip() +theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + ylab("count")+ 
scale_y_continuous(expand = c(0, 0), limits = c(0, 160)) 
```
### Plots with revised patch data
```{r}
data2 <- read.csv("Revised data with patch.csv")

## compare level

data.lvl <- data2 %>%  mutate(ground.location = strsplit(as.character(ground.location), " and ")) %>% unnest(ground.location)
data.lvl <- cbind(data.lvl[,c("uniqueID","subgenus","ground.location")])


level.n <- data.lvl %>% filter(ground.location!="N/A") %>% group_by(subgenus, ground.location) %>% count(ground.location)

lvl1 <- ggplot(level.n, aes(subgenus,fill=ground.location, y=n)) +  geom_bar(stat="identity", color="black")+scale_fill_manual(values=c("#FF9912","#BDB76B","#65909A")) +theme_bw() +coord_flip() +theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + ylab("count")+ scale_y_continuous(expand = c(0, 0), limits = c(0, 30))  +theme(legend.title=element_blank())+ theme(axis.text=element_text(colour="black", size=14),text=element_text(colour="black", size=14)) + xlab("")

data.plvl <- data2 %>%  mutate(level.pref = strsplit(as.character(level.pref), " and ")) %>% unnest(level.pref)
data.plvl <- cbind(data.plvl[,c("uniqueID","subgenus","level.pref")])
data.plvl <- data.plvl[!duplicated(data.plvl ), ]

plevel.n <- data.plvl %>% filter(level.pref!="?") %>% group_by(subgenus, level.pref) %>% count(level.pref)

lvl2 <- ggplot(plevel.n, aes(subgenus,fill=level.pref, y=n)) +  geom_bar(stat="identity", color="black")+scale_fill_manual(values=c("#FF9912","#BDB76B","#65909A")) +theme_bw() +coord_flip() +theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + ylab("count")+ scale_y_continuous(expand = c(0, 0), limits = c(0, 30)) 

require(gridExtra)

grid.arrange(lvl1,lvl2, ncol=2)



data.lnd <- data2 %>%  mutate(Site.Landscape = strsplit(as.character(Site.Landscape), " and ")) %>% unnest(Site.Landscape)
data.lnd <- cbind(data.lnd[,c("uniqueID","subgenus","Site.Landscape")])


land.n <- data.lnd %>% group_by(subgenus, Site.Landscape) %>% count(Site.Landscape)

ggplot(land.n, aes(subgenus,fill=Site.Landscape, y=n)) +  geom_bar(stat="identity", color="black") +scale_fill_manual(values=c("#BDB76B","#65909A","#FF9912","#A68064","#48426C","#B7C3D0","Grey50","Grey80")) +theme_bw() +coord_flip() +theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + ylab("count")+ 
scale_y_continuous(expand = c(0, 0), limits = c(0, 35)) 


data.plnd <- data2 %>%  mutate(preferred.landscape = strsplit(as.character(preferred.landscape), " and ")) %>% unnest(preferred.landscape)
data.plnd <- cbind(data.plnd[,c("uniqueID","subgenus","preferred.landscape")])


pland.n <- data.plnd  %>% group_by(subgenus, preferred.landscape) %>% count(preferred.landscape)

lvl2 <- ggplot(pland.n, aes(subgenus,fill=preferred.landscape, y=n)) +  geom_bar(stat="identity", color="black")+scale_fill_manual(values=c("#BDB76B","#65909A","#FBEC5D","#A68064","#48426C","#B7C3D0","#CD7054"	,"#4E78A0","Grey65"))+theme_bw() +coord_flip() +theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + ylab("count")+ scale_y_continuous(expand = c(0, 0), limits = c(0, 45)) +theme(legend.title=element_blank())+ theme(axis.text=element_text(colour="black", size=14),text=element_text(colour="black", size=14)) + xlab("")

require(gridExtra)

grid.arrange(lvl1,lvl2, ncol=2)


```

### Habitat by plot
```{r}
data2 <- read.csv("Revised data with patch.csv")

## compare level

data.lnd <- data2 %>%  mutate(preferred.landscape = strsplit(as.character(preferred.landscape), " and ")) %>% unnest(preferred.landscape)

data.lvl <- data.lnd %>%  mutate(ground.location = strsplit(as.character(ground.location), " and ")) %>% unnest(ground.location) %>% filter(ground.location!="N/A")


data.lvl <- cbind(data.lvl[,c("uniqueID","Species","preferred.landscape","ground.location")])

data.total <- data.lvl %>% group_by(ground.location, preferred.landscape) %>% count(preferred.landscape)


lnd.lvl <- ggplot(data.total, aes(preferred.landscape,fill=ground.location, y=n)) +  geom_bar(stat="identity", color="black")+scale_fill_manual(values=c("#FF9912","#BDB76B","#65909A"))+theme_bw() +coord_flip() +theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + ylab("count")+ scale_y_continuous(expand = c(0, 0), limits = c(0, 45)) +theme(legend.title=element_blank())+ theme(axis.text=element_text(colour="black", size=14),text=element_text(colour="black", size=14)) + xlab("")

```


### Clean up text
```{r}

text_df <- data_frame(text=as.character(data$Habitat.summary))

word.count <- text_df %>% unnest_tokens(word,text) %>%  dplyr::count(word, sort=T) ## count words

## list stop words
stopwords <- c(stop_words$word, "studies", "areas", "found", "also", "nest","nests","surrounding","conducted","8","6","prefers","study","included","sites","50","1000m","prefer","including","habitat","reported","habitats","possibly")
stopwords <- c(stopwords,"11","200","500","9","10","17","objects","site","suggest","type","750","stated","4","surveyed","commonly","preferred","terms","types","chosen","comparing","determine","common","fairly","energy","intake","locations","looked","maximize","mid","net","preferentially","species","randomly","nesting","constructed","landscapes","entrance","thin","forage","conflicted","regularly","lapidarius","pascuorum","withered","ecosystem","existing","lucorum","considered","low","pre","dried", "nested","ground")

## identify stop words
stop1 <- text_df %>% unnest_tokens(word,text)
stop2 <- stop1[!stop1$word %in% stopwords,]
stop3 <- stop2 %>% dplyr::count(word, sort=T)

## Remove stop words and get into long format
df <- data.frame()

for(i in 1:nrow(text_df)){
temp <- text_df[i,1]%>%  unnest_tokens(word,text) 
temp[,"id"] <- paste(i)
df <- rbind(df, temp)
}

## remove simple words
simple.text <- df[!df$word %in% stopwords,]

simple.text <- data.frame(simple.text)
simple.text[,"value"] <- 1

## replace plurals
simple.text[simple.text$word=="tussocks","word"] <- "tussock"
simple.text[simple.text$word=="fences","word"] <- "fence"
simple.text[simple.text$word=="forests","word"] <- "forest"
simple.text[simple.text$word=="cavity","word"] <- "cavities"
simple.text[simple.text$word=="grasslands","word"] <- "grassland"
simple.text[simple.text$word=="mountains","word"] <- "mountain"
simple.text[simple.text$word=="interface","word"] <- "interspace"
simple.text[simple.text$word=="boundaries","word"] <- "boundary"

simple.text <- simple.text[!duplicated(simple.text),] ## remove duplicates


## create matrix of ID by words
matrix.words <- spread(simple.text, word, value, fill=0)
rownames(matrix.words) <- matrix.words$id
matrix.words[,1:6] <- NULL
matrix.words <- cor(t(matrix.words))

## remove perfect matches
matrix.words[matrix.words==1] <- 0

matrix.words <- data.frame(matrix.words)
matrix.words[is.na(matrix.words)] <- 0
```



### Determine correlations
```{r}

## merge with original dataframe
data["id"] <- row.names(data)
matrix.words["id"] <- row.names(matrix.words)
data.text <- merge(data, matrix.words, by="id")

## long-wise data
data.text <- gather(data.text, row.id, correlation, 16:174)

## determine baseline
mean(data.text$correlation)
sqrt(var(data.text$correlation)/length(data.text$correlation))*1.96

### compare variables

## IUCN status
status <- data.text %>% group_by(IUCN.status) %>% summarize(cor=mean(correlation))

## Tounge length
toungue <- data.text %>% group_by(toungue.length) %>% summarize(cor=mean(correlation))

## subgenus
subgenus <- data.text %>% group_by(Subgenus) %>% summarize(cor=mean(correlation))

## start month
smonth <- data.text %>% group_by(Start.month) %>% summarize(cor=mean(correlation))

## end month
emonth <- data.text %>% group_by(End.month) %>% summarize(cor=mean(correlation))

## geography
geo <- data.text %>% group_by(Continent) %>% summarize(cor=mean(correlation))

## detection
detect <- data.text %>% group_by(detection.method) %>% summarize(cor=mean(correlation))


## habitat
Habitat <- data.text %>% group_by(Habitat) %>% summarize(cor=mean(correlation))
```

## wordclouds
```{r}

library(wordcloud)
library(reshape2)
simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% filter(Start.month!="?") %>%  group_by(Start.month,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~Start.month, value.var="n", fill=0) %>% comparison.cloud(max.words=100)

simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% group_by(Subgenus,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~Subgenus, value.var="n", fill=0) %>% comparison.cloud(max.words=100, title.size=1, random.order=FALSE)

simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% group_by(IUCN.status,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~IUCN.status, value.var="n", fill=0) %>% comparison.cloud(max.words=100, title.size=1.5, random.order=FALSE)

simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% group_by(toungue.length,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~toungue.length, value.var="n", fill=0) %>% comparison.cloud(max.words=100)

simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% group_by(End.month,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~End.month, value.var="n", fill=0) %>% comparison.cloud(max.words=100)

simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% group_by(Continent,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~Continent, value.var="n", fill=0) %>% comparison.cloud(max.words=100,title.size=1.5, random.order=FALSE)


simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% group_by(Continent,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~Continent, value.var="n", fill=0) %>% comparison.cloud(max.words=100,title.size=1.5, random.order=FALSE)

simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% filter(Habitat!="?") %>%  group_by(Habitat,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~Habitat, value.var="n", fill=0) %>% comparison.cloud(max.words=110,title.size=1.5, random.order=FALSE)

simple.data <- merge(data, simple.text, by="id")
cloud.data <- simple.data %>% filter(level!="?") %>% group_by(level,word) %>% summarize(n=sum(value))
cloud.data %>% acast(word~level, value.var="n", fill=0) %>% comparison.cloud(max.words=110,title.size=1.5, random.order=FALSE)
